\tool

### 2018-02-19 paper/paper.tex
Updates to heading styles

\pseudosection{Peer Interactions}
Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}. Many existing help systems simulate user-to-user recommendations to increase awareness of application tools and features.

@@

Previous work emphasizes the importance of receptivity. Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}. Our prior work defined receptiveness using two criteria introduced by Fogg: 1) demonstrating a desire and 2) familiarity with the target behavior and technology. Below we explain how \tool~was designed to recommend programming tools to software developers based on their desire and familiarity.

@@

To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends the tool \textsc{Error Prone}. \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

@@

\pseudosection{Software Engineering}

>>>>

\subsection{Peer Interactions}
Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}. Many existing help systems simulate user-to-user recommendations to increase awareness of application tools and features.

@@

Previous work emphasizes the importance of receptivity. Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}. Our prior work defined receptiveness using two criteria introduced by Fogg: 1) demonstrating a desire and 2) familiarity with the target behavior and technology. Below we explain how \tool~was designed to recommend programming tools to software developers based on their desire and familiarity. \\

@@

To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends the tool \textsc{Error Prone}. \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}. \\

@@

\subsection{Software Engineering}
